Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
pf <- read.csv("pseudo_facebook.tsv", sep="\t")



```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
install.packages('ggplot2')
library(ggplot2)
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
ggplot(data = pf, aes(x = dob_day)) + 
  geom_histogram(binwidth = 1) + 
   scale_x_continuous(breaks = 1:31) + 
   facet_wrap(~dob_month)
```

#### Let’s take another look at our plot. What stands out to you here?
Response: There is a huge representativity of 01/01. Most users apparently don't place the day and month of birth. 

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(data=pf, x=friend_count)

```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:

```{r Limiting the Axes}
qplot(data=pf, x=friend_count, xlim = c(0,1000))

```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}
qplot(x = friend_count, data = subset(pf,!is.na(gender)), binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
 by(pf$friend_count, pf$gender, summary)

```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}
qplot(x=tenure, data=pf, binwidth=30, color=I('black'), fill=I('#099DD9'))

```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x=tenure/365, data=pf, binwidth=0.25, color=I('black'), fill=I('#099DD9')) +
  scale_x_continuous(limits = c(0, 7),
                     breaks = seq(0, 7, 1))

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(x=tenure/365, 
      data=pf, 
      binwidth=0.25, 
      color=I('black'), 
      fill=I('#099DD9'), 
      xlab='Years in facebook', 
      ylab='No. of users') +
  scale_x_continuous(limits = c(0, 7),
                     breaks = seq(0, 7, 1))

```

***

### User Ages
Notes:

```{r User Ages}
qplot(x=age, 
      data=pf, 
      binwidth=2,
      color=I('black'), 
      fill=I('#099DD9'), 
      xlab='Age of user', 
      ylab='No. of users') +
  scale_x_continuous(limits = c(5, 110),
                     breaks = seq(5, 110, 2))

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:
```{r Transforming Data}

install.packages("gridExtra")
library("gridExtra")

p1 = qplot(x = friend_count, data = pf, binwidth = 10) 

p2 = qplot(x = log10(friend_count+1), data = pf, binwidth = 1) 

p3 = qplot(x = sqrt(friend_count), data = pf, binwidth = 1) 

grid.arrange(p1, p2, p3)


```

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}

p1 = qplot(x = friend_count, data = pf) 

p2 = p1 + scale_x_log10()

p3 = p1 + scale_x_log10()

grid.arrange(p1, p2, p3)

```

***


### Frequency Polygons

```{r Frequency Polygons}
qplot(x = friend_count, 
      y = ..count../sum(..count..), 
      data = subset(pf,!is.na(gender)),
      binwidth = 10,
      geom="freqpoly",
      color=gender
      ) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50)) 



```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
by(pf$www_likes, pf$gender, sum)

```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(x = gender, y= friend_count,
      data=subset(pf, !is.na(gender)),
      geom='boxplot')

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(x = gender, y= friend_count,
      data=subset(pf, !is.na(gender)  ),
      geom='boxplot',
      ylim=c(0,1000)) 
```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}
qplot(x = gender, y= friend_count,
      data=subset(pf, !is.na(gender)  ),
      geom='boxplot') +
  coord_cartesian(ylim=c(0,1000))
      


```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}
qplot(x = gender, y= friendships_initiated,
      data=subset(pf, !is.na(gender)  ),
      geom='boxplot') +
  coord_cartesian(ylim=c(0,250))

by (pf$friendships_initiated, pf$gender, summary)

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}
pf$mobile_check_in <- NA
pf$mobile_check_in <- ifelse(pf$mobile_likes>0,1,0)
pf$mobile_check_in <- factor (x=pf$mobile_check_in)

result = summary(pf$mobile_check_in)
result[["1"]]/(result[["1"]] + result[["0"]]) #My answer.

sum(pf$mobile_check_in==1)/length(pf$mobile_check_in) #course suggested.


```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!