Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))

pf <- read.delim('pseudo_facebook.tsv')

ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_histogram()
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}

pf.fc_by_age_gender <- pf %>%
  filter(!is.na(gender)) %>%
group_by(gender, age) %>%
  summarise(mean_friend_count = mean (friend_count),
            median_friend_count = median (friend_count),
            n = n()) %>%
  ungroup() %>%
  arrange(gender, age)


ggplot(aes(x=age, y=median_friend_count), data=pf.fc_by_age_gender) + geom_line(aes(color=gender))

```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
#install.packages('reshape2')
library(reshape2)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender,
                                  age ~ gender,
                                  value.var= 'median_friend_count')

head(pf.fc_by_age_gender.wide)

```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(aes(x=age, y=female/male), data= pf.fc_by_age_gender.wide) + 
  geom_line() +
  geom_hline(yintercept=1, linetype=2, alpha=0.3)

```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}

pf$year_joined <- floor(2014 - pf$tenure/365)

```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
pf$year_joined.bucket <- cut(pf$year_joined, c(2004,2009,2011,2012,2014))

table(pf$year_joined.bucket, useNA = 'ifany')
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
ggplot(aes(x=age, y=friend_count), 
       data= subset(pf,!is.na(year_joined.bucket))) + 
  geom_line(aes(color=year_joined.bucket), stat = 'summary', fun.y=median)



```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(x=age, y=friend_count), 
       data= subset(pf,!is.na(year_joined.bucket))) + 
  geom_line(aes(color=year_joined.bucket), stat = 'summary', fun.y=mean) +
  geom_line(linetype=2, stat = 'summary', fun.y=mean)


```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(pf, pf$tenure>0), summary(friend_count/tenure))

```

***

### Friendships Initiated
Notes:

What is the median friend rate? 0.220

What is the maximum friend rate? 417

```{r Friendships Initiated}
ggplot(aes(x=tenure, y=friend_count/tenure), 
       data= subset(pf,tenure>0)) + 
  geom_line(aes(color=year_joined.bucket), stat = 'summary', fun.y=mean)


ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_smooth(aes(color = year_joined.bucket))

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:



***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo <- read.csv('yogurt.csv')
str(yo)

yo$id <- factor(yo$id)
str(yo)

qplot(data=yo, x=price)
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}

yo <- transform(yo, all.purchases = strawberry + blueberry + pina.colada + plain + mixed.berry)

```

***

### Prices over Time
Notes:

```{r Prices over Time}

ggplot(aes(x=time, y=price), data=yo) +
geom_point(alpha=1/5) 


```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}

set.seed(9998)
sample.ids <- sample(yo$id, 16)

ggplot(aes(x=time, y=price),
       data = subset(yo, id %in% sample.ids)) +
 facet_wrap(~ id) +
  geom_line() +
  geom_point(aes(size= all.purchases), pch=1)

ggsave('lesson5_16houses.png')


```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
```{Scatterplot Matrix}
#install.packages("GGally")
suppressMessages(library(GGally))

theme_set(theme_minimal(20))

set_seed(1836)
pf_subset <- pf [,c(2:15)]
names(pf_subset)
ggpairs(pf_subset[sample.int(nrow(pf_subset),1000),])
```
Notes:

***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

